
\chapter{Work and Timetable}

This section outlines the timetable for the thesis. The preparatory work prior to the thesis application included researching state of the art singing voice synthesis methods and defining the research questions. The main phase of the thesis consists of implementation, evaluation and thesis writing. The singing voice synthesis method is realized in an iterative manner with the implementation going hand in hand with additional research and intermediate evaluation phases. The final evaluation phase consists of an empirical test and is intended to validate the synthesis method on a perceptual level. Writing is supposed to last one month. Two months are reserved as optional time in case any of the other phases take longer then expected. A time schedule is provided in table \ref{table:time_schedule};

\begin{table}[H]
  \centering
    \renewcommand{\arraystretch}{1.5}
  \begin{tabular}{c | c ? c | c |c | c ? c | c}
  \hline
    January & February & March & April & May & June & July & August \\\hline 
    \multicolumn{2}{c?}{Preparatory} & \multicolumn{4}{c?}{Thesis} & \multicolumn{2}{c}{Buffer}\\\hline
    Research & Proposal & \multicolumn{2}{c|}{Implementation} & \multicolumn{1}{c|}{Evaluation} & \multicolumn{1}{c?}{Writing} & \multicolumn{2}{c}{}\\\hline 
  \end{tabular}
  \caption{The proposed work time plan for the master thesis.}
  \label{table:time_schedule}
\end{table}

\section{Agenda}

This section roughly outlines the remaining tasks that comprise this thesis.

\subsection*{Preparatory Work}
\begin{itemize}
    \item Compile and summarize prior research in the field of singing voice synthesis.
    \item Write the exposé for the thesis application.
\end{itemize}

\subsection*{Implementation}
\begin{itemize}
    \item Define a method following the requirements laid out in this document.
    \item Iterative prototyping of the proposed method, conducting additional research and evaluation phases when necessary. 
    \item Source code refactoring and documentation.
\end{itemize}


\subsection*{Evaluation}
\begin{itemize}
    \item Compile material (synthesized and original audio excerpts) for the empirical test
    \item Design an empirical test / online survey
    \item Implement the online survey using tools such as LimeSurvey
    \item Run and maintain the survey
    \item Collect and analyse test results 
\end{itemize}

\subsection*{Writing}
\begin{itemize}
    \item Write the master thesis 
    \item Write German summary of the thesis
    \item Iterative proofreading and improving of content and writing
    \item Final proofreading and spellchecking
\end{itemize}
